Deep Learning Models For Identifying Crop and Field Attributes from Near Surface Cameras

### 2021-12-08 manuscript/main.tex
add package versions

Software packages used throughout the analysis include keras \citep{chollet2018-keras}, tensorflow \citep{abadi2015-tensorflow}, pandas \citep{mckinney2010-pandas}, numpy \citep{harris2020-numpy}, and pomegranate \citep{schreiber2018-pomegranate} in the python programming language \citep{python2003}. In the R language \citep{rcitation} we used the zoo \citep{zeileis2005-zoo}, tidyverse \citep{wickham2019-tidyverse}, and ggplot2 \citep{wickham2016-ggplot2} packages. All code for the analysis, as well as the final model predictions, are available in a Zenodo repository (\href{https://doi.org/10.5281/zenodo.5618316}{https://doi.org/10.5281/zenodo.5618316}).

>>>>

Software packages used throughout the analysis include Keras v2.4.3 \citep{chollet2018-keras}, TensorFlow v2.2.0 \citep{abadi2015-tensorflow}, Pandas v1.0.4 \citep{mckinney2010-pandas}, NumPy v.1.20.2 \citep{harris2020-numpy}, and Pomegranate v0.14.5 \citep{schreiber2018-pomegranate} in the Python programming language v3.7 \citep{python2003}. In the R language v4.1 \citep{rcitation} we used the zoo v1.8.0 \citep{zeileis2005-zoo}, tidyverse v1.3.1 \citep{wickham2019-tidyverse}, and ggplot2 v3.3.5 \citep{wickham2016-ggplot2} packages. All code for the analysis, as well as the final model predictions, are available in a Zenodo repository (\href{https://doi.org/10.5281/zenodo.5618316}{https://doi.org/10.5281/zenodo.5618316}).
